---
title: "PwrSEM Simulation Results"
subtitle: "Shiny App developed by Andre Wang"
output: pdf_document
date: '`r format(Sys.time(), "%B %d, %Y")`'
params:
  model:           null
  model_plot:      null
  parameter_table: null
  sample_size:     NA
  alpha_lvl:       NA
  seed:            NA
  nsims:           NA
  power_table:     null
  power_note:      null
  data:            null   # full sim_results data frame
  histop:          null   # default selected parameter name
  p_alpha:         NA
  histop_note:     null
  histoparam_note: null   # named character vector, one entry per parameter
  ci_table:        null
---

```{r setup, warning=FALSE, message=FALSE, echo=FALSE}
options(knitr.table.format = "markdown")
library(knitr)
library(ggplot2)
```

Below are the results from a power analysis for parameter estimation in structural equation modeling.
If you encounter any problems please visit our GitHub page (<https://github.com/yilinandrewang/pwrSEM>)
to raise the issue.

---

## Step 1: Analysis Model

```{r model-syntax, echo=FALSE}
if (!is.null(params$model)) {
  cat(params$model)
} else {
  cat("No model syntax available.\n")
}
```

---

## Step 2: Visualize Model

```{r model-plot, echo=FALSE, out.width="80%", fig.align="center"}
if (!is.null(params$model_plot) && file.exists(params$model_plot)) {
  knitr::include_graphics(params$model_plot)
} else {
  cat("No model plot available.\n")
}
```

---

## Step 3: Parameter Table

```{r parameter-table, echo=FALSE}
if (!is.null(params$parameter_table)) {
  kable(params$parameter_table, caption = "Parameter values used for simulation")
} else {
  cat("No parameter table available.\n")
}
```

---

## Step 4: Estimate Power

**Sample size:** `r params$sample_size`

**Alpha level:** `r params$alpha_lvl`

**Seed for simulations:** `r params$seed`

**Number of simulations:** `r params$nsims`

### Power Table

```{r power-table, echo=FALSE}
if (!is.null(params$power_table)) {
  kable(params$power_table, digits = 2, align = "l", caption = "Power Table")
  cat("\n")
  cat(paste(strwrap(params$power_note, width = 80), collapse = "\n"))
} else {
  cat("No power table available (simulations may not have been run).\n")
}
```

---

### Histograms

```{r histograms, echo=FALSE, fig.width=7, fig.height=4, warning=FALSE, message=FALSE}

# ---- helper: render both histogram panels for one parameter ----
plot_histograms_for <- function(param_name) {

  filtered <- subset(params$data, Parameter == param_name)

  if (nrow(filtered) == 0) {
    cat("No data for parameter:", param_name, "\n")
    return(invisible(NULL))
  }

  # --- p-value histogram ---
  p1 <- ggplot(filtered, aes(x = pvalue)) +
    geom_histogram(binwidth = 0.02, boundary = 0, fill = "#75dbd9", color = "white") +
    geom_vline(xintercept = params$p_alpha, color = "black", linewidth = 1) +
    scale_x_continuous(limits = c(0, 1)) +
    labs(
      title = paste("Histogram of Estimated p-Values\n(", param_name, ")", sep = ""),
      x     = "p-value of the Estimated Parameter",
      y     = "Number of Simulated Samples"
    ) +
    theme_minimal()
  print(p1)

  # Note beneath p-value histogram
  cat("\n", params$histop_note, "\n\n")

  # --- parameter estimate histogram ---

  # Try to get the population value from the parameter table
  pop_val <- tryCatch(
    params$parameter_table$Value[params$parameter_table$Parameter == param_name],
    error = function(e) NULL
  )

  # Median from power table
  median_val <- tryCatch(
    params$power_table$Median[params$power_table$Parameter == param_name],
    error = function(e) NULL
  )

  p2 <- ggplot(filtered, aes(x = est)) +
    geom_histogram(bins = 100, fill = "#75AADB", color = "white") +
    labs(
      title = paste("Histogram of Estimated Parameter Values\n(", param_name, ")", sep = ""),
      x     = "Estimated Parameter Value",
      y     = "Number of Simulated Samples"
    ) +
    theme_minimal()

  if (length(pop_val) == 1 && !is.na(pop_val)) {
    p2 <- p2 + geom_vline(xintercept = as.numeric(pop_val),
                           linetype = "solid", linewidth = 1)
  }
  if (length(median_val) == 1 && !is.na(median_val)) {
    p2 <- p2 + geom_vline(xintercept = as.numeric(median_val),
                           linetype = "dotted", linewidth = 1)
  }
  print(p2)

  # Note beneath estimate histogram
  note_vec <- params$histoparam_note
  if (!is.null(note_vec) && param_name %in% names(note_vec)) {
    cat("\n", note_vec[[param_name]], "\n\n")
  }
}

# ---- render for every parameter in the power table ----
if (!is.null(params$data) && !is.null(params$power_table)) {
  for (p in params$power_table$Parameter) {
    cat("---\n\n**Parameter:", p, "**\n\n")
    plot_histograms_for(p)
  }
} else {
  cat("No simulation data available for histograms.\n")
}
```
